Simulating NHST and TOST

### 2017-10-18 NHST_and_TOST.Rmd
NHST_TOST p-value plots, comments Lynott example

#P-value distribution TOST
hist(ptost, breaks=20, xlim=c(0,1))
sum(ptost<0.05)/nSims #Power for TOST

@@

>>>>

#P-value distribution TOST
hist(ptost, breaks=500, xlim=c(0,1))
sum(ptost<0.05)/nSims #Power for TOST

@@

#plot p-value distribution for TOST - looks peculiar
#Dat can only be so far removed from one bound, before it gets closer to the other bound. So p = 0.0000001 often not possible 
# (need to widen bounds for that, or increase N)
hist(p_sig_TOST$ptost, breaks=100)
